% Data 
## Raw data 

The data were obtained from / were organized in xx excel/csv files. The file is in the wide format where each day of assessment is in a different column, etc.

## Data wrangling

The original files were modified (see this [cheetsheet](https://github.com/rstudio/cheatsheets/raw/master/data-transformation.pdf)) as following. The names of the variables were changed to.. The original wide format was retained and will be transformed using the dplyr functions, etc.

## Glimpse 

```{r message=FALSE, warning=FALSE}
library(tidyverse)
data <- read_delim("data/data.csv", delim = ";")
glimpse(data)
```

## Variable description

- Variable1: 
  - Description 
  - Type: character
  - Unit

- Variable2: 
  - Description 
  - Type: integer
  - Unit

- Variable3: 
  - Description 
  - Type: double
  - Unit:
  
## Quick view

```{r}
data
```


## Download 

The data are deposited in xx public repositories where they can be downloaded. Check on each data repository the policies regarding data use and citation.

<img src = "https://osf.io/static/img/circle_logo.png" width = "25">
[](DOI 10.17605/OSF.IO/7D3CH) 



